---
title: "HTML Storyboard Example"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard)
```

### Embedded Leaflet Map

```{r}
library(leaflet)
m <- leaflet() 
  m %>% addProviderTiles(providers$CartoDB.Positron) %>%
  addMarkers(lng=-122.660255, lat=45.527369, popup="Where the Magic Happens")
```

***
Flexdashboard column space. We can reserve this space for summary text, etc. In the storyboard format, you're limited to one commentary column.

- Bullet points.

- More bullet points.

- Etc.

### D3 Heatmap example using car data. You can start to see how this format works a bit better for sequentially summarizing data.

```{r}
cars2017 <- read.csv("cars2017.csv", row.names=1)
library(d3heatmap)
d3heatmap(cars2017, scale="column", dendrogram="none", colors="PuBuGn")
```

***
An example of visualizing car data using d3heatmap library.


### Game of Thrones character screentimes.

```{r}
GoT <- read.csv("GoT_actors.csv")
library("plotly")

p <- plot_ly(
  GoT, 
  x = ~season.1, y = ~actor, type = 'bar', name= 'Season 1') %>%
  add_trace(x = ~season.2, name = 'Season 2') %>%
  add_trace(x = ~season.3, name = 'Season 3') %>%
  add_trace(x = ~season.4, name = 'Season 4') %>%
  add_trace(x = ~season.5, name = 'Season 5') %>%
  add_trace(x = ~season.6, name = 'Season 6') %>%
  add_trace(x = ~season.7, name = 'Season 7') %>%
  layout(xaxis = list(title = 'total screen time'), barmode = 'stack')
p
```

***
Winter is here.

